Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-23 sattose/paper.tex
Comparison added

As a result, we got the following table:

@@

>>>>

The table below shows our results.

@@

Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones. This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class unrelated even if just one of the clone instances is outside a hierarchy. It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which I do not parse, and may thus be marked UNRELATED if they are not a direct external superclass). Just like their study, ``same class'' and ``same external superclass'' are both very high. Sibling class is also very high, similar to them, but relatively it seems lower than the results they got. ``Same method'' is much higher (relatively) in our results. I think this is because the corpus I used contained a few projects with a very high in-method duplication that had a big influence on the results.
